PK object batch mode trial

### 2023-08-01 data-raw/batchMode_trial_gpm.Rmd
Added alerts column and table_format argument to coef_sd()

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442"),
                subjects.species_harmonized %in% "hamster",
                studies.administration_route_normalized %in% "iv")
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9021924")

@@

my_hess <- coef_sd(my_pk)

my_hess %>%
  rowwise() %>%
  mutate(sds = list(sds))

>>>>

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442"),
                subjects.species_harmonized %in% "hamster",
                studies.administration_route_normalized %in% "iv")
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3032179")

@@

my_hess <- coef_sd(my_pk, table_format = TRUE)

my_hess %>%
  dplyr::mutate(sds_tibble = purrr::map(sds, \(x) as.list(x) %>% as.data.frame)) %>% 
  tidyr::unnest(sds_tibble) %>%
  tidyr::pivot_longer(cols = starts_with("sigma_"),
                      names_to = "error_group",
                      values_to = "sigma.value_sd") %>%
  dplyr::filter(!is.na(sigma.value_sd)) %>%
  dplyr::mutate(coefs_tibble = purrr::map(coefs_vector, \(x) as.list(x) %>% as.data.frame)) %>% 
  tidyr::unnest(coefs_tibble) %>%
  tidyr::pivot_longer(cols = starts_with("sigma_"),
                      names_to = "error_group_value",
                      values_to = "sigma.value") %>%
  dplyr::filter(!is.na(sigma.value)) %>%
  dplyr::filter(paste0(error_group_value, "_sd") == error_group) %>%
  dplyr::select(-coefs_vector, -sds, -error_group_value) %>%
  dplyr::relocate(error_group, sigma.value, sigma.value_sd, .after = method) %>%
  View()
